---
title: "Cipro AMR model"
author: "Adewole"
format: html
editor: visual
---

## Ciprofloxacin AMR infection and assocaited regional characteristics
Logistic regression to explore the relationship between different demographic characteristics and the risk of Ciprofloxacin associated AMR infection

```{r, load libraries}
#| echo: false
#| message: false 
#| include: false

## Load libraries and import data
library(broom)
library(tidyverse)
library(car)
library(lmtest)
library(aod)
library(gtsummary)
```

You can add options to executable code like this

```{r import data}
#| echo: false
#| message: false 
#| include: false

amrData <- read.csv("data/dig_health_hub_amr.csv")
```


Data wrangling and date calculation need to be carried out

```{r}
#| echo: false
## Calculate age in years when specimen taken
amrData <- amrData %>% 
  mutate(age_years_sd = (dob %--% spec_date) %/% years(1)
         )

View(amrData)

amrData <- amrData %>% 
  mutate(
    spec_date_YMD = as.Date(amrData$spec_date),
    dob_YMD = as.Date(amrData$dob)
  )


amrData$imd <- as.factor(amrData$imd)
```

### Descriptive statistics and preliminary data exploration
```{r}
#| echo: false
# to summarise the AMR data into a table
amrData %>% tbl_summary(include=c("sex_male","age_years_sd","region","had_surgery_past_yr","ethnicity","imd","organism","coamox","cipro","gentam"),
              missing = c("no"),
              statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)"))

```

##Initial model exploring the relationship of selected demographic characteristics with cipro AMR risk 

```{r}
#| echo: false
#| message: false
cipro_region_logit <- glm(cipro ~ age_years_sd + sex_male + region + had_surgery_past_yr + ethnicity + imd,
                         data = amrData,
                         family = "binomial")

tidy(cipro_region_logit)

summary(cipro_region_logit)


glance(cipro_region_logit)

```


```{r}
#| echo: false
#| message: false
# Descriptive statistics alongside univariate regression, with no spanning header
region_model_summary <-
  amrData[c("age_years_sd", "sex_male", "region", "had_surgery_past_yr", "ethnicity", "imd")] %>%
  tbl_summary(missing = "no") %>%
  add_n() %>%
  modify_header(stat_0 ~ "**Summary Statistics**")

region_model <- tbl_regression(cipro_region_logit, exponentiate = TRUE)

tbl_merge(tbls = list(region_model_summary, region_model)) %>%
  modify_spanning_header(everything() ~ NA_character_)
```


